\chapter{Conclusions}\label{chap:Conclusion}

The main theme of our research is in understanding the geographic spread of a group; where the group can be made up of Twitter users or messages. We have explored (i) location - improving geocoding by customizing an existing geocoder as well as training a high-level geocoder with multilingual support, (ii) time - predicting whether a group is local or global and the associated UTC offset, (iii) inferring location - leverage Twitter network connections to known geo-influencers (users that cater their content to a specific geographic area). 

Google search was leveraged for identifying an initial set of geo-influencers related to a city of interest; it was shown that the geo-influencers' followers are representative of the city's users (i.e. most of the followers are physically located in the city). Location features are necessary for city-level geocoding, but time and language can also help reason about the geographic spread. Research showed that using only time-based features is enough to associate top trending topics and persons with different geographical regions. The new time-based features are not just limited to inferring location, but can also be used for inferring link creation times and for studying the evolution of influencer's popularity.

By maintaining a repository of geo-influencers it is possible to quickly leverage, as a starting point, those influencers within the geographic location of interest vs. having to discover them in a time-intensive collection from scratch (this targetted collection is 100x faster). It was also shown how the repository can be used for filtering influencers based on their audience's demographics related to location, language, gender, and ethnicity.  
This research is important because it enables multiple applications, each of which were shown in our research: (i) content recommendation, (ii) community detection, (iii) inferring the location of users based on the link structure to geo-influencers, and (iv) studying the evolution of influencer's popularity. %Main portions of the code are hosted on GitHub\footnote{https://github.com/apanasyu}.

%For understanding followers' geography, multiple approaches were explored. First using textual locations our research has illustrated how geocoding can be improved by (i) improving Google's geocoder and (ii) via a TF-IDF model that handles foreign languages and is applicable to the Twitter domain. Second through followers time and language features; where the sleep cycle identifies the most probable region of the world and language further limits the set of possible countries (we are not aware of any other research that utilizes the sleep cycle for helping predict a geographic region). Third through link structure; it was illustrated how using an initial set of influencers set A, communities can be established from influencers' followers, and using these communities additional influencers set B can be discovered. 