\begin{thebibliography}{200}
\bibitem{-1}Karami, Amir, et al. "Twitter and research: a systematic literature review through text mining." IEEE Access 8 (2020): 67698-67717.\label{appendix:0.1}
\bibitem{0}Antonakaki, Despoina, Paraskevi Fragopoulou, and Sotiris Ioannidis. "A survey of Twitter research: Data model, graph structure, sentiment analysis and attacks." Expert Systems with Applications 164 (2021): 114006.\label{appendix:0.2}

\bibitem{1}Zheng, Xin, Jialong Han, and Aixin Sun. ``A survey of location prediction on Twitter.`` IEEE Transactions on Knowledge and Data Engineering (2018).\label{appendix:1.1}
\bibitem{2}Graham, Mark, Scott A. Hale, and Devin Gaffney. ``Where in the world are you? Geolocation and language identification in Twitter.`` The Professional Geographer 66.4 (2014): 568-578.\label{appendix:1.2}
\bibitem{3}Mislove, Alan, et al. ``Understanding the Demographics of Twitter Users.`` ICWSM 11.5th (2011): 25.\label{appendix:1.3}
\bibitem{4}Stephens, Monica, and Ate Poorthuis. ``Follow thy neighbor: Connecting the social and the spatial networks on Twitter.`` Computers, Environment and Urban Systems 53 (2015): 87-95.\label{appendix:1.4}
\bibitem{5}Beauchamp, Nicholas. ``Predicting and interpolating state‐level polls using Twitter textual data.`` American Journal of Political Science 61.2 (2017): 490-503.\label{appendix:1.5}
\bibitem{6}Byrd, Kenny, et al. ``Mining Twitter data for influenza detection and surveillance.`` Proceedings of the International Workshop on Software Engineering in Healthcare Systems. ACM, 2016.\label{appendix:1.6}
\bibitem{7}Zubiaga, Arkaitz, et al. ``Towards real-time, country-level location classification of worldwide tweets.`` IEEE Transactions on Knowledge and Data Engineering 29.9 (2017): 2053-2066.\label{appendix:1.7}
\bibitem{8}Jurgens, David, et al. ``Geolocation Prediction in Twitter Using Social Networks: A Critical Analysis and Review of Current Practice.`` ICWSM 15 (2015): 188-197.\label{appendix:1.8}
\bibitem{9}Wong, Charlene A., et al. ``Twitter sentiment predicts Affordable Care Act marketplace enrollment.`` Journal of medical Internet research 17.2 (2015).\label{appendix:1.9}
\bibitem{10}Matci, Dilek Küçük, and Uğur Avdan. ``Address standardization using the natural language process for improving geocoding results.`` Computers, Environment and Urban Systems (2018).\label{appendix:1.10}
\bibitem{11}Jurgens, David. ``That's What Friends Are For: Inferring Location in Online Social Media Platforms Based on Social Relationships.`` ICWSM 13.13 (2013): 273-282.\label{appendix:1.11}
\bibitem{12}Malik, Momin M., et al. ``Population bias in geotagged tweets.`` People 1.3,759.710 (2015): 3-759.\label{appendix:1.12}
\bibitem{13}Tasse, Dan, et al. ``State of the Geotags: Motivations and Recent Changes.`` ICWSM. 2017.\label{appendix:1.13}
\bibitem{14}Prasetyo, Philips., et al. ``On analyzing geotagged tweets for location-based patterns.`` Proceedings of the 17th International Conference on Distributed Computing and Networking. ACM, 2016.\label{appendix:1.14}
\bibitem{15}Laniado, David, et al. ``The Impact of Geographic Distance on Online Social Interactions.`` Information Systems Frontiers(2017): 1-16.\label{appendix:1.15}
\bibitem{16}Singh, Sushant K. ``Evaluating two freely available geocoding tools for geographical inconsistencies and geocoding errors.`` Open Geospatial Data, Software and Standards 2.1 (2017): 11\label{appendix:1.16}
\bibitem{17}Vincenty, Thaddeus. ``Direct and inverse solutions of geodesics on the ellipsoid with application of nested equations.`` Survey review 23.176 (1975): 88-93.\label{appendix:1.17}
\bibitem{18}Miyazaki, Taro, et al. ``Twitter Geolocation using Knowledge-Based Methods.`` Proceedings of the 2018 EMNLP Workshop W-NUT: The 4th Workshop on Noisy User-generated Text. 2018.\label{appendix:1.18}

\bibitem{19}Riquelme, Fabián, and Pablo González-Cantergiani. ``Measuring user influence on Twitter: A survey.`` Information Processing \& Management 52.5 (2016): 949-975.\label{appendix:2.1}
\bibitem{20}Bouros, Panagiotis, Dimitris Sacharidis, and Nikos Bikakis. ``Regionally influential users in location-aware social networks.`` Proceedings of the 22nd ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems. ACM, 2014.\label{appendix:2.2}
\bibitem{21}Li, Guoliang, et al. ``Efficient location-aware influence maximization.`` Proceedings of the 2014 ACM SIGMOD international conference on Management of data. ACM, 2014.\label{appendix:2.3}
\bibitem{22}Darmon, David, Elisa Omodei, and Joshua Garland. ``Followers are not enough: A multifaceted approach to community detection in online social networks.`` PloS one 10.8 (2015): e0134860.\label{appendix:2.4}
\bibitem{23}Java A, Song X, Finin T, Tseng B (2009) Why we twitter: an analysis of a microblogging community. In: Advances in Web Mining and Web Usage Analysis, Springer. pp. 118–138.\label{appendix:2.5}
\bibitem{24}Wang, T.-C.; Phoa, F.K.H.: A scanning method for detecting clustering pattern of both attribute and structure in social networks. Phys. A Stat. Mech. Appl. 445, 295–309 (2016)\label{appendix:2.6}
\bibitem{25}Yang, J.; McAuley, J.; Leskovec, J.: Community detection in networks with node attributes. In: IEEE 13th International Conference on Data mining (ICDM), pp. 1151–1156. IEEE (2013)\label{appendix:2.7}
\bibitem{26}Zhang, F.; Li, J.; Li, F.; Xu, M.; Xu, R.; He, X.: Community detection based on links and node features in social networks. In: He, X., Luo, S., Tao, D., Xu, C., Yang, J., Hasan, M.A. (eds.) MultiMedia Modeling. MMM 2015. Lecture Notes in Computer Science, vol. 8935. Springer, Cham (2015)\label{appendix:2.8}
\bibitem{27}Mucha, Peter J., et al. ``Community structure in time-dependent, multiscale, and multiplex networks.`` science 328.5980 (2010): 876-878.\label{appendix:2.9}
\bibitem{28}Hossain, Nabil, et al. ``Inferring fine-grained details on user activities and home location from social media: Detecting drinking-while-tweeting patterns in communities.`` arXiv preprint arXiv:1603.03181 (2016).\label{appendix:2.10}
\bibitem{29}Gurajala, Supraja, et al. ``Fake Twitter accounts: profile characteristics obtained using an activity-based pattern detection approach.`` Proceedings of the 2015 International Conference on Social Media \& Society. ACM, 2015.\label{appendix:2.11}
\bibitem{30}Bakillah, Mohamed, Ren-Yu Li, and Steve HL Liang. ``Geo-located community detection in Twitter with enhanced fast-greedy optimization of modularity: the case study of typhoon Haiyan.`` International Journal of Geographical Information Science 29.2 (2015): 258-279.\label{appendix:2.12}
\bibitem{31}Maleewong, Krissada. ``An analysis of influential users for predicting the popularity of news tweets.`` Pacific Rim International Conference on Artificial Intelligence. Springer, Cham, 2016.\label{appendix:2.13}
\bibitem{32}Xiao, Feng, Tomoya Noro, and Takehiro Tokuda. ``Finding News-Topic Oriented Influential Twitter Users Based on Topic Related Hashtag Community Detection.`` J. Web Eng. 13.5\&6 (2014): 405-429.\label{appendix:2.14}
\bibitem{33}Cha, Meeyoung, et al. ``Measuring user influence in twitter: The million follower fallacy.`` Icwsm 10.10-17 (2010): 30.\label{appendix:2.15}
\bibitem{34}Jabeur, Lamjed Ben, Lynda Tamine, and Mohand Boughanem. ``Active microbloggers: Identifying influencers, leaders and discussers in microblogging networks.`` International Symposium on String Processing and Information Retrieval. Springer, Berlin, Heidelberg, 2012.\label{appendix:2.16}
\bibitem{35}Rout, Dominic, et al. ``Where's@ wally?: a classification approach to geolocating users based on their social ties.`` Proceedings of the 24th ACM Conference on Hypertext and Social Media. ACM, 2013.\label{appendix:2.19}
\bibitem{36}Freeman, Linton C. ``Centrality in social networks conceptual clarification.`` Social networks 1.3 (1978): 215-239.\label{appendix:2.22}
\bibitem{37}Gayo-Avello, Daniel. ``Nepotistic relationships in twitter and their impact on rank prestige algorithms.`` Information Processing \& Management 49.6 (2013): 1250-1280.\label{appendix:2.23}
\bibitem{38}Weng, Jianshu, et al. ``Twitterrank: finding topic-sensitive influential twitterers.`` Proceedings of the third ACM international conference on Web search and data mining. ACM, 2010.\label{appendix:2.24}
\bibitem{39}Silva, Arlei, et al. ``ProfileRank: finding relevant content and influential users based on information diffusion.`` Proceedings of the 7th Workshop on Social Network Mining and Analysis. ACM, 2013.\label{appendix:2.25}
\bibitem{40}Wei, Hong, Jagan Sankaranarayanan, and Hanan Samet. ``Measuring Spatial Influence of Twitter Users by Interactions.`` Proceedings of the 1st ACM SIGSPATIAL Workshop on Analytics for Local Events and News. ACM, 2017.\label{appendix:2.26}
\bibitem{41}Subrahmanian, V. S., et al. ``The DARPA Twitter bot challenge.`` Computer 49.6 (2016): 38-46.\label{appendix:2.27}

\bibitem{42} Li, Yuchen, et al. ``Influence maximization on social graphs: A survey.`` IEEE Transactions on Knowledge and Data Engineering (2018).\label{appendix:3.1}
\bibitem{43} Su, Sen, et al. ``Location‐aware targeted influence maximization in social networks.`` Journal of the Association for Information Science and Technology 69.2 (2018): 229-241.\label{appendix:3.2}
\bibitem{44} Panasyuk, Aleksey, Edmund Yu, and Kishan Mehrotra. ``Augmenting Google Search in Ranking Twitter Users.`` Semantic Computing (ICSC), 2019 IEEE 13th International Conference on. IEEE, 2019.\label{appendix:3.3}
\bibitem{45} Li, Yuchen, Dongxiang Zhang, and Kian-Lee Tan. ``Real-time targeted influence maximization for online advertisements.`` Proceedings of the VLDB Endowment 8.10 (2015): 1070-1081.\label{appendix:3.5}
\bibitem{46} Seabrook, Elizabeth M., Margaret L. Kern, and Nikki S. Rickard. ``Social networking sites, depression, and anxiety: a systematic review.`` JMIR mental health 3.4 (2016).\label{appendix:3.6}
\bibitem{47} Aghababaei, Somayyeh, and Masoud Makrehchi. ``Mining social media content for crime prediction.`` 2016 IEEE/WIC/ACM International Conference on Web Intelligence (WI). IEEE, 2016.\label{appendix:3.7}
\bibitem{48} Guo, Weisi, et al. ``Understanding happiness in cities using Twitter: Jobs, children, and transport.`` 2016 IEEE International Smart Cities Conference (ISC2). IEEE, 2016.\label{appendix:3.8}
\bibitem{49} Panasyuk, Aleksey, Edmund Yu, and Kishan Mehrotra. ``Improving Geocoding for City-level Locations.`` Semantic Computing (ICSC), 2019 IEEE 13th International Conference on. IEEE, 2019.\label{appendix:3.11}
\bibitem{50} Compton, Ryan, David Jurgens, and David Allen. ``Geotagging one hundred million twitter accounts with total variation minimization.`` Big Data (Big Data), 2014 IEEE International Conference on. IEEE, 2014.\label{appendix:3.13}
\bibitem{51} Kariryaa, Ankit, et al. ``Defining and Predicting the Localness of Volunteered Geographic Information using Ground Truth Data.`` Proc. CHI. Vol. 18. 2018.\label{appendix:3.14}
\bibitem{52} Leetaru, Kalev, et al. ``Mapping the global Twitter heartbeat: The geography of Twitter.`` First Monday 18.5 (2013).\label{appendix:3.15}
\bibitem{53} Ferrara, Emilio, et al. ``The rise of social bots.`` Communications of the ACM 59.7 (2016): 96-104.\label{appendix:3.17}
\bibitem{54} Webber, William, Alistair Moffat, and Justin Zobel. ``A similarity measure for indefinite rankings.`` ACM Transactions on Information Systems (TOIS) 28.4 (2010): 20.)\label{appendix:3.21}
\bibitem{55} B. Han and A. Srinivasan, 'Your friends have more friends than you do: Identifying influential mobile users through random-walk sampling,' in  Proc. 13th MOBIHOC, 2012, pp. 5--14.\label{appendix:3.22}
\bibitem{56} Wang, Yufeng, et al. ``PPRank: economically selecting initial users for influence maximization in social networks.`` IEEE Systems Journal 11.4 (2017): 2279-2290.\label{appendix:3.23}
\bibitem{57} Li, Xiao, et al. ``Community-based seeds selection algorithm for location aware influence maximization.`` Neurocomputing 275 (2018): 1601-1613.\label{appendix:3.24}

\bibitem{58.1} Çıtlak, Oğuzhan, Murat Dörterler, and İbrahim Alper Doğru. "A survey on detecting spam accounts on Twitter network." Social Network Analysis and Mining 9.1 (2019): 1-13.\label{appendix:bookCh2.1}
\bibitem{58.2} Wu, Tingmin, et al. "Twitter spam detection: Survey of new approaches and comparative study." Computers \& Security 76 (2018): 265-284.\label{appendix:bookCh2.2}
\bibitem{58.3} Yang, Kai-Cheng, et al. "Scalable and generalizable social bot detection through data selection." Proceedings of the AAAI Conference on Artificial Intelligence. Vol. 34. No. 01. 2020.\label{appendix:bookCh2.3}

\bibitem{59} Craswell, Nick, Arjen P. De Vries, and Ian Soboroff. ``Overview of the TREC 2005 Enterprise Track.`` Trec. Vol. 5. 2005.\label{appendix:bookCh2}
\bibitem{60} Husain, Omayma, et al. ``Expert Finding Systems: A Systematic Review.`` Applied Sciences 9.20 (2019): 4250.\label{appendix:bookCh3}
\bibitem{61} T. Lappas, K. Liu, and E. Terzi. A survey of algorithms and systems for expert location in social networks. In Social Network Data Analytics. Springer, 2011.\label{appendix:bookCh4}
\bibitem{62} Page, Lawrence, et al. The PageRank citation ranking: Bringing order to the web. Stanford InfoLab, 1999.\label{appendix:bookCh5}
\bibitem{63} Kleinberg, Jon M. ``Authoritative sources in a hyperlinked environment.`` Journal of the ACM (JACM) 46.5 (1999): 604-632.\label{appendix:bookCh6}
\bibitem{64} Romero, Daniel M., et al. ``Influence and passivity in social media.`` Joint European Conference on Machine Learning and Knowledge Discovery in Databases. Springer, Berlin, Heidelberg, 2011.\label{appendix:bookCh8}
\bibitem{65} Pal, Aditya, and Scott Counts. ``Identifying topical authorities in microblogs.`` Proceedings of the fourth ACM international conference on Web search and data mining. 2011. \label{appendix:bookCh9}
\bibitem{66} Ghosh, Saptarshi, et al. ``Cognos: crowdsourcing search for topic experts in microblogs.`` Proceedings of the 35th international ACM SIGIR conference on Research and development in information retrieval. 2012.\label{appendix:bookCh10}
\bibitem{67} Cheng, Zhiyuan, et al. ``Who is the barbecue king of texas? A geo-spatial approach to finding local experts on twitter.`` Proceedings of the 37th international ACM SIGIR conference on Research {\&} development in information retrieval. 2014.\label{appendix:bookCh11}
\bibitem{68} Mourad, Ahmed, et al. ``A practical guide for the effective evaluation of twitter user geolocation.`` ACM Transactions on Social Computing 2.3 (2019): 1-23.
\label{appendix:bookCh13}
\bibitem{69} Li, Wen, Carsten Eickhoff, and Arjen P. de Vries. ``Geo-spatial domain expertise in microblogs.`` European Conference on Information Retrieval. Springer, Cham, 2014.
\label{appendix:bookCh15}
\bibitem{70} Li, Wen, Carsten Eickhoff, and Arjen P. de Vries. ``Probabilistic local expert retrieval.`` European Conference on Information Retrieval. Springer, Cham, 2016.\label{appendix:bookCh16}
\bibitem{71} Niu, Wei, Zhijiao Liu, and James Caverlee. ``On local expert discovery via geo-located crowds, queries, and candidates.`` ACM Transactions on Spatial Algorithms and Systems (TSAS) 2.4 (2016): 1-24.\label{appendix:bookCh17}

\bibitem{71.2} Yochum, Phatpicha, et al. "Linked open data in location-based recommendation system on tourism domain: A survey." IEEE Access 8 (2020): 16409-16439.\label{appendix:bookChNew3}
\bibitem{71.3} Luceri, Luca, et al. "Measurement and control of geo-location privacy on Twitter." Online social networks and media 17 (2020): 100078.\label{appendix:bookChNew4}
\bibitem{71.4} Zola, Paola, Costantino Ragno, and Paulo Cortez. "A Google Trends spatial clustering approach for a worldwide Twitter user geolocation." Information Processing \& Management 57.6 (2020): 102312.\label{appendix:bookChNew5}
\bibitem{71.5} Singh, Jyoti Prakash, et al. "Event classification and location prediction from tweets during disasters." Annals of Operations Research 283.1 (2019): 737-757.\label{appendix:bookChNew7}
\bibitem{71.6} Paule, Jorge David Gonzalez, Yeran Sun, and Yashar Moshfeghi. "On fine-grained geolocalisation of tweets and real-time traffic incident detection." Information Processing \& Management 56.3 (2019): 1119-1132.\label{appendix:bookChNew8}

\bibitem{72} Inkpen, Diana, et al. ``Location detection and disambiguation from twitter messages.`` Journal of Intelligent Information Systems 49.2 (2017): 237-253.\label{appendix:bookCh23}
\bibitem{73} Efron B., R. J. Tibshirani. ``An introduction to the bootstrap``, Chapman \& Hall;CRC 1998.\label{appendix:bookCh28}
\bibitem{74} Panasyuk, Aleksey, Kishan G. Mehrotra, and Edmund Szu-Li Yu. ``Automated Location-Aware Influencer Evaluation.`` Proceedings of the 3rd International Conference on Vision, Image and Signal Processing. 2019.\label{appendix:bookCh29}

\bibitem{75} Meeder, Brendan, et al. ``We know who you followed last summer: inferring social link creation times in twitter.`` Proceedings of the 20th international conference on World wide web. ACM, 2011.\label{appendix:5.15}
\bibitem{76} H. Kwak, H. Chun, and S. Moon. Fragile online relationship: a first look at unfollow dynamics in Twitter. In Proc. of ACM CHI’11, Vancouver, BC, Canada, 2011.\label{appendix:5.16}

\bibitem{77} Lau, Jey Han, et al. ``End-to-end network for twitter geolocation prediction and hashing.`` arXiv preprint arXiv:1710.04802 (2017).\label{appendix:6b.14}
\bibitem{78} Ebrahimi, Mohammad, et al. ``A unified neural network model for geolocating twitter users.`` Proceedings of the 22nd Conference on Computational Natural Language Learning. 2018.\label{appendix:6b.15}
\bibitem{79} Zannettou, Savvas, et al. ``Disinformation warfare: Understanding state-sponsored trolls on Twitter and their influence on the web.`` Companion proceedings of the 2019 world wide web conference. 2019.\label{appendix:6b.16}
\bibitem{80} Rehurek, Radim. ``Subspace tracking for latent semantic analysis.`` European Conference on Information Retrieval. Springer, Berlin, Heidelberg, 2011.\label{appendix:6b.17}

\bibitem{81} Nguyen, Dong, et al. ```` How old do you think I am?`` A study of language and age in Twitter.`` Seventh International AAAI Conference on Weblogs and Social Media. 2013.\label{appendix:4.2}
\bibitem{82} Burger, John D., et al. ``Discriminating gender on Twitter.`` Proceedings of the conference on empirical methods in natural language processing. Association for Computational Linguistics, 2011.\label{appendix:4.3}
\bibitem{83} Hargittai, Eszter, and Eden Litt. ``The tweet smell of celebrity success: Explaining variation in Twitter adoption among a diverse group of young adults.`` New media \& society 13.5 (2011): 824-842.\label{appendix:4.4}
\bibitem{84} Li, Linna, Michael F. Goodchild, and Bo Xu. ``Spatial, temporal, and socioeconomic patterns in the use of Twitter and Flickr.`` cartography and geographic information science 40.2 (2013): 61-77.\label{appendix:4.5}
\bibitem{85} Flekova, Lucie, Daniel Preoţiuc-Pietro, and Lyle Ungar. ``Exploring stylistic variation with age and income on twitter.`` Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics (Volume 2: Short Papers). Vol. 2. 2016.\label{appendix:4.6}
\bibitem{86} Chang, Jonathan, et al. ``ePluribus: Ethnicity on Social Networks.`` ICWSM 10 (2010): 18-25.\label{appendix:4.7}
\bibitem{87} Ciot, Morgane, Morgan Sonderegger, and Derek Ruths. ``Gender inference of Twitter users in non-English contexts.`` Proceedings of the 2013 Conference on Empirical Methods in Natural Language Processing. 2013.\label{appendix:4.8}
\bibitem{88} Culotta, Aron, Nirmal Ravi Kumar, and Jennifer Cutler. ``Predicting the Demographics of Twitter Users from Website Traffic Data.`` AAAI. 2015.\label{appendix:4.9}
\bibitem{89} Golbeck, Jennifer, and Derek Hansen. ``A method for computing political preference among Twitter followers.`` Social Networks 36 (2014): 177-184.\label{appendix:4.10}
\bibitem{90} Mohammady, Ehsan, and Aron Culotta. ``Using county demographics to infer attributes of twitter users.`` Proceedings of the joint workshop on social dynamics and personal attributes in social media. 2014.\label{appendix:4.12}

\bibitem{93} Nechaev, Yaroslav, Francesco Corcoglioniti, and Claudio Giuliano. ``SocialLink: exploiting graph embeddings to link DBpedia entities to Twitter profiles.`` Progress in Artificial Intelligence 7.4 (2018): 251-272.\label{appendix:4.15}

\iffalse
\bibitem{94} Asur, Sitaram, and Bernardo A. Huberman. ``Predicting the future with social media.`` Proceedings of the 2010 IEEE/WIC/ACM International Conference on Web Intelligence and Intelligent Agent Technology-Volume 01. IEEE Computer Society, 2010.\label{appendix:4.16}

\bibitem{95} Chi, Feng, and Nathan Yang. ``Twitter adoption in Congress.`` Review of Network Economics 10, no. 1 (2010).\label{appendix:5.1}
\bibitem{96} Williams, Christine B., and Girish J. Gulati. ``Communicating with Constituents in 140 Characters or Less.`` (2010).\label{appendix:5.2}
\bibitem{97} Lassen, David S., and Adam R. Brown. ``Twitter The Electoral Connection?.`` Social Science Computer Review 29, no. 4 (2011): 419-436.\label{appendix:5.3}
\bibitem{98} Golbeck, Jennifer, Justin M. Grimes, and Anthony Rogers. ``Twitter use by the US Congress.`` Journal of the American Society for Information Science and Technology 61, no. 8 (2010): 1612-1621.\label{appendix:5.4}
\bibitem{99} Furnas, G. W., et al. ``Statistical semantics: Analysis of the potential performance of keyword information systems.`` Human factors in computer systems. Ablex Publishing Corp., 1984.\label{appendix:5.5}
\bibitem{100} Manning, C. D., Raghavan, P., \& Schutze, H. Introduction to information retrieval. Vol. 1. Cambridge: Cambridge university press, 2008.\label{appendix:5.6}
\bibitem{101} Salton, Gerard, Anita Wong, and Chung-Shu Yang. ``A vector space model for automatic indexing.`` Communications of the ACM 18.11 (1975): 613-620.\label{appendix:5.7}
\bibitem{102} Deerwester, Scott C., et al. ``Indexing by latent semantic analysis.`` JASIS 41.6 (1990): 391-407.\label{appendix:5.8}
\bibitem{103} Blei, D.M., Ng, A.Y., Jordan, M.I.: Latent Dirichlet allocation. JMLR (2003)\label{appendix:5.9}
\bibitem{104} T. Hofmann. Probabilistic latent semantic indexing. Proceedings of the Twenty-Second Annual International SIGIR Conference, 1999.\label{appendix:5.10}
\bibitem{105} Wallach, Hanna M., David M. Mimno, and Andrew McCallum. ``Rethinking LDA: Why Priors Matter.`` NIPS. Vol. 22. 2009.\label{appendix:5.11}
\bibitem{106} Zhao, Wayne Xin, et al. ``Comparing twitter and traditional media using topic models.`` Advances in Information Retrieval. Springer Berlin Heidelberg, 2011. 338-349.\label{appendix:5.13}
\bibitem{107} Baccianella, Stefano, Andrea Esuli, and Fabrizio Sebastiani. ``SentiWordNet 3.0: An Enhanced Lexical Resource for Sentiment Analysis and Opinion Mining.`` LREC. Vol. 10. 2010.\label{appendix:5.14}
\bibitem{108} Rejaie, Reza, et al. ``Sizing up online social networks.`` Network, IEEE 24.5 (2010): 32-37.\label{appendix:5.17}
\bibitem{109} Liu, Yabing, Chloe Kliman-Silver, and Alan Mislove. ``The Tweets They Are a-Changin: Evolution of Twitter Users and Behavior.`` ICWSM. Vol. 30. 2014. 5-314.\label{appendix:5.18}
\bibitem{110} Tanaka, Atsushi, Hikaru Takemura, and Keishi Tajima. ``Why you follow: a classification scheme for twitter follow links.`` Proceedings of the 25th ACM conference on Hypertext and social media. ACM, 2014.\label{appendix:5.19}
\bibitem{111} Mikolov, Tomas, et al. ``Distributed representations of words and phrases and their compositionality.`` Advances in neural information processing systems. 2013.\label{appendix:5.20}
\bibitem{112} Deriu, Jan, et al. ``SwissCheese at SemEval-2016 Task 4: Sentiment classification using an ensemble of convolutional neural networks with distant supervision.`` Proceedings of SemEval (2016): 1124-1128.\label{appendix:5.21}
\bibitem{113} Philip J. Stone, Dexter C. Dunphy, Marshall S. Smith, and Daniel M. Ogilvie. 1966. The General Inquirer: A Computer Approach to Content Analysis. MIT Press.\label{appendix:5.22}
\bibitem{114} Janyce Wiebe, Theresa Wilson, and Claire Cardie (2005). Annotating expressions of opinions and emotions in language. Language Resources and Evaluation, volume 39, issue 2-3, pp. 165-210.\label{appendix:5.23}
\bibitem{115} Hu, Minqing, and Bing Liu. ``Mining and summarizing customer reviews.`` Proceedings of the tenth ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2004.\label{appendix:5.24}
\bibitem{116} Mohammad, Saif M., and Peter D. Turney. ``Emotions evoked by common words and phrases: Using Mechanical Turk to create an emotion lexicon.`` Proceedings of the NAACL HLT 2010 workshop on computational approaches to analysis and generation of emotion in text. Association for Computational Linguistics, 2010.\label{appendix:5.25}
\bibitem{117} Nielsen, Finn Årup. ``A new ANEW: Evaluation of a word list for sentiment analysis in microblogs.`` arXiv preprint arXiv:1103.2903 (2011).\label{appendix:5.26}
\bibitem{118} Bradley, Margaret M., and Peter J. Lang. Affective norms for English words (ANEW): Instruction manual and affective ratings. Technical report C-1, the center for research in psychophysiology, University of Florida, 1999.\label{appendix:5.27}
\fi

\iffalse
\bibitem{1} Kursuncu, Ugur, et al. ``Predictive Analysis on Twitter: Techniques and Applications.`` Emerging Research Challenges and Opportunities in Computational Social Network Analysis and Mining. Springer, Cham, 2019. 67-104.\label{appendix:6.1}
\bibitem{2} Shi, Lei, et al. ``Predicting US primary elections with Twitter.`` URL: http://snap. stanford. edu/social2012/papers/shi. pdf (2012).\label{appendix:6.2}
\bibitem{3} Heredia, Brian, Joseph D. Prusa, and Taghi M. Khoshgoftaar. ``Location-Based Twitter Sentiment Analysis for Predicting the US 2016 Presidential Election.`` The Thirty-First International Flairs Conference. 2018.\label{appendix:6.3}
\bibitem{4} Karami, Amir, London S. Bennett, and Xiaoyun He. ``Mining public opinion about economic issues: Twitter and the us presidential election.`` International Journal of Strategic Decision Sciences (IJSDS) 9.1 (2018): 18-28.\label{appendix:6.4}
\bibitem{5} Ebrahimi, Monireh, Amir Hossein Yazdavar, and Amit Sheth. ``Challenges of sentiment analysis for dynamic events.`` IEEE Intelligent Systems 32.5 (2017): 70-75.\label{appendix:6.5}
\bibitem{6} A. Sheth, H. Purohit, G. A. Smith, J. Brunn, A. Jadhav, P. Kapanipathi, C. Lu, and W. Wang, ``Twitris: A System for Collective Social Intelligence,`` Encyclopedia of Social Network Analysis and Mining, 2018.\label{appendix:6.6}
\bibitem{7} Darwish, Kareem, Walid Magdy, and Tahar Zanouda. ``Trump vs. Hillary: What went viral during the 2016 US presidential election.`` International conference on social informatics. Springer, Cham, 2017.\label{appendix:6.7}
\bibitem{8} Kennedy, Courtney, et al. ``An evaluation of the 2016 election polls in the United States.`` Public Opinion Quarterly 82.1 (2018): 1-33.\label{appendix:6.8}
\bibitem{9} L. Chen, et al., ``Extracting Diverse Sentiment Expressions with Target-Dependent Polarity from Twitter,`` Sixth International AAAI Conference on Weblogs and Social Media, 2012.\label{appendix:6.9}
\bibitem{10} Gayo-Avello, Daniel. ```` I Wanted to Predict Elections with Twitter and all I got was this Lousy Paper``--A Balanced Survey on Election Prediction using Twitter Data.`` arXiv preprint arXiv:1204.6441 (2012).\label{appendix:6.10}
\bibitem{11} Wu, Tingmin, et al. ``Twitter spam detection: Survey of new approaches and comparative study.`` Computers \& Security 76 (2018): 265-284.\label{appendix:6.11}
\bibitem{13} Zhang, Lei, Shuai Wang, and Bing Liu. ``Deep learning for sentiment analysis: A survey.`` Wiley Interdisciplinary Reviews: Data Mining and Knowledge Discovery 8.4 (2018): e1253.\label{appendix:6.13}
\bibitem{14} A. Makazhanov and D. Rafiei, ``Predicting Political Preference of Twitter Users,`` Social Network Analysis and Mining, 2014.\label{appendix:6.14}
\bibitem{15} Barberá, Pablo. ``Birds of the same feather tweet together: Bayesian ideal point estimation using Twitter data.`` Political Analysis 23.1 (2015): 76-91.\label{appendix:6.15}
\bibitem{16} R. Cohen and D. Ruths, ``Classifying Political Orientation on Twitter: It’s Not Easy!`` in ICWSM, 2013\label{appendix:6.16}
\bibitem{17} Howard, Philip N., et al. ``Junk news and bots during the US election: What were Michigan voters sharing over Twitter.`` Computational Propaganda Research Project, Oxford Internet Institute, Data Memo 2017.1 (2017).\label{appendix:6.17}
\bibitem{18} Boshmaf, Yazan, et al. ``The socialbot network: when bots socialize for fame and money.`` Proceedings of the 27th annual computer security applications conference. ACM, 2011.\label{appendix:6.18}
\bibitem{20} Ratkiewicz, J., Conover, M., Meiss, M., Gonçalves, B., Flammini, A. and Menczer, F. Detecting and tracking political abuse in social media. In Proceedings of the 5th International AAAI Conference on Weblogs and Social Media (2011). 297–304.\label{appendix:6.20}
\bibitem{22} Webb, Steve, James Caverlee, and Calton Pu. ``Social Honeypots: Making Friends With A Spammer Near You.`` CEAS. 2008.\label{appendix:6.22}
\bibitem{23} Freitas, Carlos, et al. ``Reverse engineering socialbot infiltration strategies in twitter.`` Advances in Social Networks Analysis and Mining (ASONAM), 2015 IEEE/ACM International Conference on. IEEE, 2015.\label{appendix:6.23}
\bibitem{24} Cao, Qiang, et al. ``Aiding the detection of fake accounts in large scale social online services.`` Proceedings of the 9th USENIX conference on Networked Systems Design and Implementation. USENIX Association, 2012.\label{appendix:6.24}


\bibitem{1} Bradford, Roger B. ``An empirical study of required dimensionality for large-scale latent semantic indexing applications.`` Proceedings of the 17th ACM conference on Information and knowledge management. 2008.\label{appendix:7.1}

\fi
\end{thebibliography}